### 2015-07-09 text/ms.Rmd
More edits

Whereas averages or weighted averages may improve predictions over any single model, they may not optimally leverage available data. The truth does not necessarily lie in the middle of multiple model predictions, some models may perform better than others in certain conditions, and the covariance between models may contain information that can improve predictive accuracy. We can exploit these characteristics by using the predictions from a group of models as inputs into a separate statistical model. This technique, sometimes called 'superensemble' modelling, is common in climate and weather forecasting [e.g. @krishnamurti1999; @yun2005; @mote2015]. The superensemble is fit to some training dataset where outcomes are well known and used to predict on a dataset of interest. For example, @krishnamurti1999 combined predictions of wind and precipitation in Asian monsoons via a superensemble regression fit to observed data. Their superensemble was considerably more accurate than any individual prediction or weighted average of predictions.

@@

* *CMSY* (catch-MSY) implements a stock-reduction analysis with Schaefer biomass
  dynamics [@martell2013]. It requires a prior distribution for $r$ and assigns
  a prior to the relative proportion of biomass at the end compared to unfished
  biomass (depletion) based on the percentage of maximum catch at the end of the
  time series. Our version of the model was modified from @martell2013 to
  generate biomass trends from all viable $r$-$K$ pairs and produced an estimate of
  $B/B_\mathrm{MSY}$ from the geometric mean trend.

@@

*TODO: Coilin: How ensembles can help understand mechanistic underpinnings of individual models*
Beyond predictive performance, superensembles can help understand mechanistic
underpinnings of individual models. 
First, at a most basic level, superensembles that allow for nonlinear
relationships can describe at what ranges of a prediction a certain model is
most informative. For example, we can see that SSCOM is most effective at
distinguishing low values of $B/B_\mathrm{MSY}$ (Fig. S4).
Second, the interaction between superensemble predictors can highlight
under what conditions certain models perform best. 
For instance, SAY SOMETHING ABOUT FIG S5 or FIG S6.
*discover surprises: counterintuitive relationships and interactions*
*can dig into surprising conditions and learn about why certain models fail; potentially learn how to improve models*
*can learn under what conditions certain models perform well*

>>>>

Whereas averages or weighted averages may improve predictions over any single model, they may not optimally leverage available data. The truth does not necessarily lie in the middle of multiple model predictions, some models may perform better than others in certain conditions, and the covariance between models may contain information that can improve predictive accuracy. We can exploit these characteristics by using the predictions from a group of models as inputs into a separate statistical model. This technique, sometimes called 'superensemble' modelling [@krishnamurti1999], is common in climate and weather forecasting [e.g. @yun2005; @mote2015]. The superensemble is fit to some training dataset where outcomes are well known and used to predict on a dataset of interest. For example, @krishnamurti1999 combined predictions of wind and precipitation in Asian monsoons via a superensemble regression fit to observed data. Their superensemble was considerably more accurate than any individual prediction or weighted average of predictions.

@@

* *CMSY* (catch-MSY) implements a stock-reduction analysis with Schaefer biomass
  dynamics [@martell2013]. It requires a prior distribution for $r$ and assigns
  a prior to the relative proportion of biomass at the end compared to unfished
  biomass (depletion) based on the percentage of maximum catch at the end of the
  time series. Our version of the model was modified from @martell2013 to
  generate biomass trends from all viable $r$-$K$ pairs and produce an estimate of
  $B/B_\mathrm{MSY}$ from the median trend.

@@

*TODO: Coilin: How ensembles can help understand mechanistic underpinnings of individual models*
Beyond predictive performance, superensembles can help understand mechanistic
underpinnings of individual models. 
First, superensembles that allow for nonlinear
relationships can describe at what ranges of a prediction a certain model is
most informative. For example, we can see that SSCOM is most effective at
distinguishing low values of $B/B_\mathrm{MSY}$ (Fig. S4).
Second, the interaction between superensemble predictors can highlight
under what conditions certain models perform best. 
For instance, SAY SOMETHING ABOUT FIG S5 or FIG S6.
*discover surprises: counterintuitive relationships and interactions*
*can dig into surprising conditions and learn about why certain models fail; potentially learn how to improve models*
*can learn under what conditions certain models perform well*
